%-------------------------
% Resume in Latex
% Author : Asim Shrestha
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames]{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

\hypersetup{
  colorlinks=true,
  linkcolor=NavyBlue,
  urlcolor=NavyBlue,
}

\let\oldhref\href
\renewcommand{\href}[2]{\oldhref{#1}{\uline{#2}}}


\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{%
  \item \small #1%
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
  \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{#1} & #4 \\
  \textit{\small#3} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{#1} & #4 \\
  \textit{\small#3} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{%
  \resumeItem{#1}{#2}%
}

\renewcommand{\labelitemi}{\scriptsize$\bullet$}
\renewcommand{\labelitemii}{\scriptsize$\bullet$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{%
  \begin{itemize}[itemsep=0.15em, topsep=0.1em, parsep=0pt, partopsep=0pt]%
}
\newcommand{\resumeItemListEnd}{%
  \end{itemize}%
}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
  \vspace*{-2.5em}  % Moves header upwards; tweak value to taste
  \begin{center}
  {\huge \textbf{Asim Shrestha}}\\[2pt]
  \small
  (415) 815-7736 \textbar\ %
  \href{mailto:asim.shrestha@hotmail.com}{asim.shrestha@hotmail.com} \textbar\ %
  \faLinkedinSquare\ \href{https://www.linkedin.com/in/a-shrestha/}{a-shrestha} \textbar\ %
  \faGithub\ \href{https://github.com/asim-shrestha}{asim-shrestha}
  \end{center}
  \vspace{-0.15in}



%--------TECHNICAL SKILLS------------
  \section{Technical Skills}
  \resumeSubHeadingListStart
  \item{\small{
    \textbf{Languages:} {Python, Typescript, Rust, Kotlin, HTML, CSS, SQL} \\
    \textbf{Libraries \& frameworks:} {FastAPI, Next.js, React, OpenTelemetry, Protobuff, Terraform, Prisma, SQLAlchemy} \\
    \textbf{Software \& tools:} {AWS, Docker, PostgreSQL, MySQL, Kafka, Redis, Clickhouse, Firecracker, Grafana, RabbitMQ, Git} \\
    \textbf{Other skills:} {System Design, CI/CD, OOP, Functional Programming, DevOps, Algorithms, Testing, Architecture} \\
  }}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
  \section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {{Reworkd} (\href{https://www.reworkd.ai/}{Website})}{San Francisco, CA}
  {Co-founder \& CEO}{Mar. 2023 -- Current}
  \resumeItemListStart
  \resumeItem
  {Raised \$4M from tier one investors like Y Combinator, Paul Graham, SV Angel, AI Grant, and more to build browser-based LLM agents.}
  \resumeItem
  {Launched one of the first available web agents in AgentGPT and scaled to 1M users, 35K stars on GitHub, and over \$1M in annual recurring revenue. (\href{https://github.com/reworkd/AgentGPT}{GitHub})}
  \resumeItem
  {Architected arbitrary code execution service via Firecracker microVMs and AWS bare metal instances to sandbox and execute LLM generated code with millisecond latency overhead.}
  \resumeItem
  {Designed headless browser infrastructure using an L7 MiTM proxy sidecar to allow for sub second anti-bot evasion while handling 1TB+ of network traffic every week.}
  \resumeItem
  {Developed novel OCR based page parsing algorithm to convert webpage screenshots into whitespace-structured text to enhance LLM context. Took success rate in internal code generation benchmarks from 50\% to 98\%. (\href{https://github.com/reworkd/tarsier}{GitHub})}
  \resumeItem
  {Created an AST-based post-processing system to automatically correct LLM-generated code by dynamically optimizing invalid selectors, overwriting hallucinated methods, and injecting missing syntax.}
  \resumeItemListEnd

  \resumeSubheading
  {Amazon Web Services}{Vancouver, BC}
  {Software Development Engineer}{Feb. 2022 -- Mar. 2023}
  \resumeItemListStart
  \resumeItem
  {Helped lead intra-org decoupling initiatives on the RDS Platform team to load manage/scale internal services and tighten security posture for RDS disaster scenarios.}
  \resumeItem
  {Engineered zero downtime major version upgrades (PG14 to PG17) for metadata stores powering RDS. Shed 10\% in CPU utilization and up to 20ms in critical query latency across regions like us-east-1.}
  \resumeItem
  {Built ReCRUX in my spare time, a browser extension which added key features to our existing code review platform like persisting file view state, comment/file links, and other QOL improvements. Used internally by over 5K engineers.}
  \resumeItemListEnd

  \resumeSubheading
  {BC Cancer Research Center}{Vancouver, BC}
  {Full Stack Engineer Intern}{Jan. 2021 -- Apr. 2021}
  \resumeItemListStart
  \resumeItem
  {Open sourced RT-Utils, a Python library used to facilitate the creation of 3D medical image files from machine learning segmentation masks. Used by 100s of researchers from MIT, Waterloo, UCLA and more. (\href{https://github.com/qurit/rt-utils}{GitHub}, \href{https://arxiv.org/pdf/2405.06184}{Paper})}
  \resumeItem
  {Worked closely with Medical researchers to develop a medical data file anonymization and distribution application with extremely fine grained controls for anonymization configuration.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
  \section{Projects}
  \resumeSubHeadingListStart
  \resumeSubheading
  {{Webboy} ({\href{https://github.com/asim-shrestha/webboy}{GitHub}})}{}
  {Gameboy emulator}{Sept. 2025 -- Nov. 2025}
  \resumeItemListStart
  \resumeItem
  {Cycle accurate Gameboy emulator built in rust with full emulation of the CPU, MMU, PPU, MBC, and more.}
  \resumeItemListEnd

  \resumeSubheading
  {Bilby Compiler}{}
  {Custom programming language}{Apr. 2021 -- Aug. 2021}
  \resumeItemListStart
  \resumeItem
  {Custom programming language compiler built with Java, covering parsing, lexical analysis, semantic analysis, and intermediate code generation to support language features like arrays, conditionals, loops, and functions.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
  \section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Simon Fraser University}{Vancouver, BC}%
  {Bachelor of Science in Computer Science}{Sep. 2017 -- Dec. 2021}
  \resumeItemListStart
  \resumeItem{\textbf{Awards:} Graduated first class with distinction; President's and Dean's Honour roll.}
  \resumeItem{\textbf{CGPA:} 4.04/4.33 with academic performance in the top 5\% in the school of computer science.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
